non_phylo_analyses

### 2018-04-07 reports/non_phylo_model.Rmd
removed species which aren't species based on Jetz's tree. Makes sense to keep the same species set for both phylo and non-phylo models, I think.

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-inner_join(response_variables,traits)
```

>>>>

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-left_join(traits,response_variables, by="binom") %>%
  filter(SCIENTIFIC_NAME_tree != "not_treated_as_species")
```
